Modelling the emergence of whisker barrels

### 2019-12-19 paper/briefpaper/brief.tex
fdsf

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{./MainFig.png}
\end{center}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1 by \cite{zheng_signal_2001}, with black lines to delineate barrels and to measure departure ($\delta$) from a perfect Voronoi tesselation. Right shows the initial distribution of axon branching density ($a$) for one thalamocortical projection and two molecular guidance fields ($\rho$). \textbf{B} The strength of interaction $\gamma$ for each of 41 projections with field $\rho_1$ and $\rho_2$ are indicated by the lengths of green and blue arrows respectively, assuming that similar fields aligned to the posterior-anterior and medial-lateral axes in the ventroposterior medial nucleus of the thalamus are sampled at the locations of barreloid centers (reconstructed from \cite{haidarliu_size_2001}). \textbf{C} Simulation results for parameters $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$ and $\delta{t}=0.0001$. Colours indicate the thalamic projection for which the connection density is maximal, black lines delineate boundaries, and overlaid contours show $c>0.5$. \textbf{D} The Honda $\delta$ metric (red dots; see \cite{senft_mouse_1991}) measures departure from a Voronoi tesselation (dotted line corresponds to the barrels in $A$), and $\eta$ (black squares) measures the correspondence between the real and simulated barrel shapes (the product of the sum of squared differences between real and simulated centers and the sum of differences in area; units mm$^4$). \textbf{E.} Guidance fields and emergent barrel pattern in a Fgf8 misexpression experiment (c.f. \cite{assimacopoulos_fibroblast_2012}), simulated by reflecting $\rho_1$ about the anterior-posterior axis. All scale bars 1mm.}
\label{fig:main}
\end{figure*}

@@

Moreover, the present results confirm that such structures can emerge without requiring the pre-specification of centre-points by as yet undetermined additional developmental mechanisms.

%The model also shows that the shape of the barrels may be primarily determined by the competitive and cooperative interactions between cells relative to the shape of the cortical field boundary. And that somatotopic map formation does not require the pre-specification of centre-points by as yet undetermined additional developmental mechanisms.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{./MainFig.pdf}
\end{center}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1 by \cite{zheng_signal_2001}, with black lines to delineate barrels and to measure departure (Honda-$\delta$; see \cite{senft_mouse_1991}) from a perfect Voronoi tesselation. Right shows the initial distribution of axon branching density ($a$) for one thalamocortical projection, and two molecular guidance fields ($\rho$). \textbf{B} The strengths of interaction $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41 projections by the lengths of green and blue arrows respectively, assuming that similar fields aligned to the posterior-anterior and medial-lateral axes in the ventroposterior medial nucleus of the thalamus are sampled at the locations of putative barreloid centers (reconstructed from \cite{haidarliu_size_2001}). \textbf{C} Simulation results for parameters $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$, $\epsilon=150$ and $\delta{t}=0.0001$. Colours indicate the thalamic projection for which the connection density is maximal, black lines delineate boundaries, and overlaid contours show $c>0.5$. \textbf{D} Red dots show the Honda-$\delta$ metric obtained from simulation approaching that obtained from barrels in \textbf{A} (dotted line);  black squares measure the correspondence between the real and simulated barrel shapes, $\eta$ (the product of the sum of squared differences between real and simulated centers and the sum of differences in area; units mm$^4$). \textbf{E.} Guidance fields and emergent barrel pattern in a Fgf8 misexpression experiment (c.f. \cite{assimacopoulos_fibroblast_2012}), simulated by reflecting $\rho_1$ at the join ($\epsilon=80$). All scale bars 1mm.}
\label{fig:main}
\end{figure*}

@@

Moreover, the present results confirm that somatotopic map formation does not require the pre-specification of centre-points by as yet undetermined additional developmental mechanisms.
